A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-03-17 doc/paper.tex
Related work work.

\section{Introduction}
% no \IEEEPARstart
Business and research alike owe their debts to spreadsheets, the table-based interface which empowers users to organize and manipulate huge bodies of data [citation for definition]. Their allure is in their versatility: while the novice end user can work without a deep knowledge of programming, the expert can expedite their work with a variety of built-in operations, or functions.\footnote{https://support.office.com/en-us/article/Excel-functions-alphabetical-b3944572-255d-4efb-bb96-c6d90033e188} As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million U.S. workers could be using them, including the 25 million who would be writing programs out of the functions included (Scaffidi citations).\par

Considering this ubiquity, it's crucial to get spreadsheets right. Our failures in their use can be ruinous, as in 2012 when the influential findings on economic growth were reversed by a selection error [Enron paper], among other horror stories.\footnote{http://www.eusprig.org/horror-stories.htm}

Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts. Collections like EUSES[cite], FUSE[cite], and the Enron corpus[cite] have already enabled fruitful work across the field: [EXAMPLES FROM RESEARCH]. A number of these studies focus on discovering which built-in functions are the most common (enabling something). \par

@@

\section{Related Work}
Spreadsheets, being a core component of business that they are, have prompted the development of many tools to evaluate them and their many qualities. [RESEARCH ON NON-VISUAL ANALYSIS TOOLS] \par
Furthermore, this tool comes from a line of spreadsheet visualization tools before it, each with a different focus. For example, Breviz, developed by Hermans and colleagues, uses visualization to illustrate workbook dataflow to address the need for a clearly communicable representation of spreadsheets as they move from person to person. \par
Other studies focus on API and built-in function use outside the domain of spreadsheets. [RESEARCH ON API STUDIES]

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

\section{Introduction}
% no \IEEEPARstart
Business and research alike owe their debts to spreadsheets, the table-based interface which empowers users to organize and manipulate huge bodies of data [citation for definition]. Their allure is in their versatility: while the novice end user can work without a deep knowledge of programming, the expert can expedite their work with a variety of built-in operations, or functions.\footnote{https://support.office.com/en-us/article/Excel-functions-alphabetical-b3944572-255d-4efb-bb96-c6d90033e188} As such, it should be of little surprise when Scaffidi and colleagues estimated that by 2012, over 50 million U.S. workers could be using them, including the 25 million who would be writing programs out of the functions included \cite{scaffidi2005estimating}.\par

Considering this ubiquity, it's crucial to get spreadsheets right. Our failures in their use can be ruinous, as in 2012 when the influential findings on economic growth were reversed by a selection error, among other horror stories.\footnote{http://www.eusprig.org/horror-stories.htm}

Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts. Collections like EUSES \cite{fisher2005euses}, FUSE \cite{barik2015fuse}, and the Enron corpus \cite{hermans2015enron} have already enabled fruitful work across the field, such as detecting code smells in spreadsheets \cite{hermans2012detecting} \cite{cunha2012smellsheet}.  \par

@@

\section{Related Work}
This tool comes from a line of spreadsheet visualization tools before it, each with a different focus. Some tools, such as Igarashi and colleague's fluid visualizations \cite{igarashi1998fluid}, seek to visualize the hidden formulas within a spreadsheet by imposing the dataflow graphs over the cells. Likewise, Clermont \cite{clermont2003scalable} (and Hipfl \cite{hipfl2008using}, who extended his work) explored various ways of visualizing groups of related cells through similar functions, neighbors, or references. Others focus on creating visualizations outside of the sheets: Hermans and colleagues address a spreadsheet programmer's information needs through their work on the tools GyroSAT \cite{hermans2011supporting} and Breviz \cite{hermans2011breviz} to make dataflow diagrams of individual spreadsheets. These, however, tend to focus on individual spreadsheets and not bodies of them. \par
Nevertheless, other studies and tools focus more on evaluating the content of the cells therein. (Hermans, Smellsheet) \par
Other studies focus on API and built-in function use outside the domain of spreadsheets. [RESEARCH ON API STUDIES]

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}
%
%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%
%
%\end{thebibliography}
